Spike Spectra for Recurrences

### 2022-11-16 Manuscript/entropy-1919488  proof/entropy-1919488.tex
corrected links

\dataavailability{The study that we present here is available as a fully reproducible code base
**Repository will be published and cited here, when accepted** and the method
will be available in the Julia language (https://zenodo.org/record/7328513#.Y3Vb4VLMJqw) and as a MATLAB\textsuperscript{\textregistered} toolbox 
(https://zenodo.org/record/7328499#.Y3Vb91LMJqw).}

>>>>

\dataavailability{The study that we present here is available as a fully reproducible code base
**Repository will be published and cited here, when accepted** and the method
will be available in the Julia language (https:doi.org/10.5281/zenodo.7328513) and as a MATLAB\textsuperscript{\textregistered} toolbox 
(https:doi.org/10.5281/zenodo.7328499).}
